A mathematical framework for understanding microbiome differential-abundance methods

### 2021-05-04 index.Rmd
Update title, abstract, and readme

---
title: "Characterizing and mitigating the effects of experimental bias on differential (absolute) abundance analysis in microbiome studies"
author: "Michael R. McLaren"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [main.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: mikemc/bda-theory
description: "Mathematical theory of the effects of experimental bias on differential (relative and absolute) abundance analysis in microbiome studies."
---

@@

This monograph develops a mathematical theory of the effects of protocol- and taxon-specific experimental bias on various types of differential (relative and absolute) abundance analyses in microbiome studies and uses it to formulate several mitigation strategies.

>>>>

---
title: "A mathematical framework for understanding microbiome differential-abundance methods"
author: "Michael R. McLaren"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [main.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: mikemc/bda-theory
description: "A mathematical framework for understanding (relative and absolute) microbiome differential-abundance methods"
---

@@

This manuscript develops a mathematical framework for understanding microbiome differential-abundance analysis; 
specifically, how taxonomic bias and other complications of real microbiome measurement can distort the results of commonly-used methods.
This framework predicts that certain approaches to relative and absolute differential abundance are more sensitive to bias than others.
The effects of bias can be mitigated by choosing an insensitive approach or performing a calibration procedure using targeted abundance measurements of one or more specific taxa.
